Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-06-06 supplement/05_calibration_data.Rmd
relabel export figures
stringi to top

```{r eval=TRUE}
# for data handling
library(data.table)
library(atlastools)

@@

```{r}
library(stringi)
data_res <- data_unproc[stri_detect(tID, regex = "(WP)")]
```

@@

# save figure
ggsave(figure_res_patch,
  filename = "figures/fig_06.png",
  height = 170, width = 170, units = "mm"
)
```

>>>>

```{r eval=TRUE}
# for data handling
library(data.table)
library(atlastools)
library(stringi)

@@

```{r}
data_res <- data_unproc[stri_detect(tID, regex = "(WP)")]
```

@@

# save figure
ggsave(figure_res_patch,
  filename = "figures/fig_07.png",
  height = 170, width = 170, units = "mm"
)
```
